Matching Bullets

### 2015-12-13 imaging-paper.Rnw
odd mis-match updated

\begin{figure}[hbtp]
\begin{subfigure}[t]{.49\textwidth}
\caption{Maximal number of CMS between unknown Bullet D land 5 and all of the 120 other (known) lands. For two lands the number of maximum CMS is high. }
<<cms, echo=FALSE, fig.width=7, fig.height=3.5, out.width='\\textwidth'>>=
load("data-15-25/unkn17.RData")
cmsdist <- sapply(reslist, function(x) x$maxCMS)

@@

\begin{figure}[hbtp]
<<strange-res, echo=FALSE, fig.width=7, fig.height=3.25, out.width='\\linewidth', warning=FALSE>>=
load("data-15-25/unkn37.RData")
res <- reslist[[60]]

print(ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), ymin=-6, ymax=5, data=res$lines, alpha=0.2, show.legend=FALSE) +
  geom_line(aes(x = y, y = l30, linetype = bullet),  data = res$bullets) +
#  geom_hline(yintercept = res$threshold) +
#  geom_hline(yintercept = - res$threshold) +
#  scale_colour_brewer("",palette="Set1") +
  scale_linetype_discrete("") + ylab("") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1), legend.justification=c(1,1)) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match)))
@
\caption{\label{fig:mismatch}Known mismatch with a relatively large number of maximal consecutive matching striae (twelve) in the middle. Visual inspection easily reveals this as mismatch. }
\end{figure}

>>>>

\begin{figure}[hbtp]
\begin{subfigure}[t]{.49\textwidth}
\caption{Maximal number of CMS between unknown Bullet D land 5 and all of the 120 other (known) lands. For two lands the number of maximum CMS is high. }
<<cms, echo=FALSE, fig.width=7, fig.height=3.5, out.width='\\textwidth'>>=
load("data-new-25-25/unkn17.RData")
cmsdist <- sapply(reslist, function(x) x$maxCMS)

@@

\begin{figure}[hbtp]
<<strange-res, echo=FALSE, fig.width=7, fig.height=3.25, out.width='\\linewidth', warning=FALSE>>=
load("data-25-25/unkn47.RData")
res <- reslist[[106]]
splits <- strsplit(as.character(res$bullets$bullet), split="/")
last <- sapply(splits, function(x) x[length(x)])
res$bullets$bullet <- gsub(".x3p","", last)

print(ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), ymin=-6, ymax=5, data=res$lines, alpha=0.2, show.legend=FALSE) +
  geom_line(aes(x = y, y = l30, linetype = bullet),  data = res$bullets) +
  scale_linetype_discrete("") + ylab("") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1), legend.justification=c(1,1)) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match)))
@
\caption{\label{fig:mismatch}Known mismatch with a relatively large number of maximal consecutive matching striae (twelve) in the middle. The pattern in the middle does look surprisingly similar, however the outer ends of the crosscuts easily reveals this as mismatch. }
\end{figure}
